Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-16 talk/dls2012/paper.tex
some details

\revc{
I would have liked to have benchmark results for some larger applications.
When is this optimization effective on a large scale, if ever?
}
\cfbolz{I don't actually know. Does anybody?}

@@

\revd{
This paper is relatively short, and could be significantly improved with a
couple of pages of additional information about the details of the benchmarks
-- both on the Python and on the C side.
}

@@

\subsection{Python}
The Python interpreter of the RPython framework is a complete Python
version 2.7 compatible interpreter. A set of numerical
calculations were implemented in both Python, C and Lua and their
runtimes are compared in Figure~\ref{fig:benchmarks}.\footnote{
    The benchmarks and the scripts to run them can be found in the repository for this paper:
    \texttt{https://bitbucket.org/pypy/extradoc/src/ tip/talk/dls2012/benchmarks}
}

@@

In addition we also ported the 
SciMark\footnote{\texttt{http://math.nist.gov/scimark2/}} benchmakts to python, and compared 
their runtimes with the already existing Lua and C implementations. 
This port was performed after the release of the pypy used to run the benchmarks which means that 
these benchmarks have not influenced the pypy implementation.
SciMark consists of

>>>>

@@

@@

\subsection{Python}
The Python interpreter of the RPython framework is a complete Python
version 2.7 compatible interpreter. A set of numerical
calculations were implemented in both Python, C and Lua and their
runtimes are compared in Figure~\ref{fig:benchmarks}.\footnote{
    The benchmarks and the scripts to run them can be found in the repository for this paper:
    \texttt{https://bitbucket.org/pypy/extradoc/src/ tip/talk/dls2012/benchmarks}
}
For benchmarks using larger Python applications the times are unaffected or
slightly improved by the loop optimization of this paper.

@@

In addition we also ported the 
SciMark\footnote{\texttt{http://math.nist.gov/scimark2/}} benchmarts to Python, and compared
their runtimes with the already existing
Lua\footnote{\texttt{http://luajit.org/download/scimark.lua}} and C
implementations.

SciMark consists of:
